Cell type assignments for SCPCP000015

### 2025-02-07 analyses/cell-type-ewings/exploratory_analysis/08-merged-celltypes.Rmd
fix some legend titles

ComplexHeatmap::Heatmap(
    auc_mtx,
    # set the color scale based on min and max values
    col = circlize::colorRamp2(seq(min(auc_mtx), max(auc_mtx), length = 2), colors = c("white", "#00274C")),
    border = TRUE,
    ## Row parameters
    cluster_rows = TRUE,
    row_title = "Combined cell types",
    row_title_side = "left",
    row_names_side = "left",
    row_dend_side = "right",
    row_names_gp = grid::gpar(fontsize = 10),
    ## Column parameters
    column_title = "MSigDB gene set",
    cluster_columns = TRUE,
    show_column_names = TRUE,
    column_names_gp = grid::gpar(fontsize = 8),
    heatmap_legend_param = list(
      title = "Mean expression"
    )
  )

@@

single_annotation_heatmap(
  all_info_df, 
  exp_columns = mean_exp_columns, 
  cell_type_column = "final_lumped", 
  legend_title = "AUC"
)
```

>>>>

ComplexHeatmap::Heatmap(
    auc_mtx,
    # set the color scale based on min and max values
    col = circlize::colorRamp2(seq(min(auc_mtx), max(auc_mtx), length = 2), colors = c("white", "#00274C")),
    border = TRUE,
    ## Row parameters
    cluster_rows = TRUE,
    row_title = "Combined cell types",
    row_title_side = "left",
    row_names_side = "left",
    row_dend_side = "right",
    row_names_gp = grid::gpar(fontsize = 10),
    ## Column parameters
    column_title = "MSigDB gene set",
    cluster_columns = TRUE,
    show_column_names = TRUE,
    column_names_gp = grid::gpar(fontsize = 8),
    heatmap_legend_param = list(
      title = "Mean AUC"
    )
  )

@@

single_annotation_heatmap(
  all_info_df, 
  exp_columns = mean_exp_columns, 
  cell_type_column = "final_lumped", 
  legend_title = "Mean expression"
)
```
